---
title: "p8105_hw2_hq2163_hanbo"
author: "Hanbo Qiu"
date: "September 30, 2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```

#Problem 1
##Import and clean NYC Transit csv files
Import my first csv (NYC_Transit_Subway_Entrance_And_Exit_Data.csv) and clean it.

```{r}
nyc_sub  = read_csv(file = "./data/NYC_Transit_Subway_Entrance_And_Exit_Data.csv") %>% 
  janitor::clean_names() %>% 
  select(line:entry, vending, ada) %>% 
  mutate(entry = recode(entry, "YES" = TRUE, "NO" = FALSE)
  )
```

##Write a short paragraph about this dataset 

The original dataset contains variables related to subway station name, location and each entrance and exit for each subway station in NYC. I import the dataset, convert  column names to lower snake case, retain column including "line, station, name, station latitude/longitude, routes served, entry, vending, entrance type, and ADA compliance" and convert the entry variable from character to a logical variable.The dimension of the dataset is `r nrow(nyc_sub)`*`r ncol(nyc_sub)`. The data provided includes columns route1 to route10, which list all routes served by a station entrance/exit. This isn't a "tidy" format, and should be restructured accordingly.

##Answer questions using these data

```{r}
dist_stat = distinct(nyc_sub, line, station_name)
n_dist_stat = nrow(dist_stat)

dist_stat_ada = subset(nyc_sub, ada == TRUE, select = c(station_name, line))
n_stat_ada = n_distinct(dist_stat_ada)

dist_stat_vend = subset(nyc_sub, vending == "YES", select = c(line, station_name))
n_stat_vend = n_distinct(dist_stat_vend)
prop_stat_vend = (n_dist_stat-n_stat_vend)/n_dist_stat
```

There are `r n_dist_stat` distinct stations. Among them, `r n_stat_ada` are ADA compliant. The proportion of station entrances / exits without vending allow entrance is `r prop_stat_vend`.

##Reformat data
Reformat data using route number and route name. Caculate distinct stations serve the A train and number of distinct stations which serve A train is ADA compliant.

```{r}
nyc_route = gather(nyc_sub, key = route_number, value = route_name, route1: route11)
stat_a = subset(nyc_route,route_name == "A")
dist_stat_a = distinct(stat_a, line, station_name)
n_dist_stat_a = nrow(dist_stat_a)

stat_a_ada = subset(stat_a, ada == TRUE)
a_stat_ada = distinct(stat_a_ada, line, station_name)
n_a_stat_ada = nrow(a_stat_ada)
```

There are `r n_dist_stat_a` distinct stations serve the A train. Of the stations that serve the A train, ADA compliant is `r n_a_stat_ada`.

#Problem 2
##Read and clean the Mr. Trash Wheel sheet

```{r}
library(readxl)
trash_wheel = read_excel("./data/HealthyHarborWaterWheelTotals2017-9-26.xlsx", 
                         sheet = "Mr. Trash Wheel", 
                         range = cell_cols("A:N")) %>% 
   janitor::clean_names() %>% 
   filter(!is.na(dumpster)) %>% 
   mutate(sports_balls = as.integer(round(sports_balls, digits = 0)))
```
##Read and clean precipitation data

```{r}
precip_2017 = read_excel("./data/HealthyHarborWaterWheelTotals2017-9-26.xlsx",
                         sheet = "2017 Precipitation",
                         skip = 1,
                         n_max = 12) %>% 
  janitor::clean_names() %>%
  mutate(year = 2017) %>%
  filter(!is.na(total)) %>% 
  select(year, everything()) 

precip_2016 = read_excel("./data/HealthyHarborWaterWheelTotals2017-9-26.xlsx",
                         sheet = "2016 Precipitation",
                         skip = 1,
                         n_max = 12) %>% 
  janitor::clean_names() %>%
  mutate(year = 2016) %>%
  filter(!is.na(total)) %>% 
  select(year, everything()) 

precip_16_17 = bind_rows(precip_2017,precip_2016) %>% 
  mutate(month = factor(month, levels = 1:12, labels = month.name),
         month = as.character(month)
         )

n_trash_wheel = nrow(trash_wheel)
n_precip_16_17 = nrow(precip_16_17)

total_precip_2017 = sum(precip_2017$total)

ball_2016 = subset(trash_wheel, year == 2016, select = sports_balls)
median_ball = median(ball_2016$sports_balls)
```
The number of observations in Trash Wheel sheet is `r n_trash_wheel` and the number of observations in precipitation data is `r n_precip_16_17`. Some key variables are year, month because they are the connection between two database. The total precipitation in 2017 is `r total_precip_2017`. The median number of sports balls in a dumpster in 2016 is `r median_ball`.
